Tutorial 2b

### 2025-07-09 Tutorial_2a.Rmd
change model results and sizes figs 3 and 4
increase size Figures 3 and 4

```{r epred-grand-diff-plot}
 p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.4, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-0.5,0.3)) +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin", y = "difference in predicted hazard") +
  #ggtitle("Grand average marginal effect") +
  facet_wrap(~contrast)

@@

```{r save-fig-revision, eval=F}
ggsave("Tutorial_2_Bayesian/figures/Revision_results_hazard.png", width = 10, height = 22, dpi = 800)
```

>>>>

```{r epred-grand-diff-plot}
 p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.4, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-0.5,0.3)) +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_fill_manual(values=c("#D95F02FF", "#7570B3FF")) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin", y = "difference in predicted hazard") +
  #ggtitle("Grand average marginal effect") +
  facet_wrap(~contrast)

@@

```{r save-fig-revision, eval=F}
ggsave("Tutorial_2_Bayesian/figures/Revision_results_hazard.png", width = 14, height = 20, dpi = 800)
```

### 2025-07-09 Tutorial_2b.Rmd
Small corrections
increase size Figures 3 and 4

```{r grand-ame-plot}
p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.5, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
 # stat_halfeye(point_interval = "mean_qi",.width=c(.8,.95))+
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-1,1)) +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin", y = "difference in predicted ca") +
#  ggtitle("Grand average marginal effect") +
  facet_wrap(~contrast)
p11
```

@@

```{r save-fig-revision, eval=F}
ggsave("Tutorial_2_Bayesian/figures/Revision_results_ca.png", width = 10, height = 22, dpi = 800)
```

>>>>

```{r grand-ame-plot}
p11 <- ggplot(epreds_grand_diffs, aes(x=timebin, y=diff_ca, 
                       fill=contrast)) +
  stat_lineribbon(alpha = 0.5, 
                  point_interval = "mean_qi",
                  .width=c(.8,.95)) +
  geom_hline(yintercept = 0, 
             color = "red", 
             lty = 3) +
  scale_y_continuous(limits=c(-1,1)) +
  scale_x_discrete(labels = str_c("(",(c(6:15)-1)*40,",",c(6:15)*40,"]"), breaks = 6:15) +
  scale_fill_manual(values=c("#D95F02FF", "#7570B3FF")) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(x = "time bin", y = "difference in predicted ca") +
  facet_wrap(~contrast)
p11
```

@@

```{r save-fig-revision, eval=F}
ggsave("Tutorial_2_Bayesian/figures/Revision_results_ca.png", width = 14, height = 20, dpi = 800)
```
